A survey of HTTP caching implementations on the open Semantic Web

### 2015-02-18 sanity/rebuttal.txt

I would like to thank the reviewers for their extensive reviews.

I would first like to address the main point of critisism voiced
mainly by Review 4 but also by Review 2, that the survey is of a very
limited "Semantic Web" and so is unlikely to be generalizeable.

This critisism is very valid and taken to heart. Indeed, this survey
is not meant to be generalizeable beyond the current state of the art,
as I find it quite likely that the current state must change in order
for the Semantic Web to be successful. The scope of the survey is a
snapshot, confined to what this community can reasonably do something
about, and currently, we are such a tiny fraction of the Web, that we
have to understand the Web better to succeed.

This survey is not intended as means to understand what the rest of
the Web is doing right and wrong, that wisdom is available elsewhere
in the broader literature, but as I tried not to pass judgement,
except in a small number of cases where current practice is clearly
severely flawed, it was not within my scope, nor the pagelimit, to
cite.

The intention is mostly to have empirical research to counter
statements like "it is no point in using caches when evaluating SPARQL
queries, since no endpoints are exposing them".

### 2015-02-18 sanity/rebuttal.txt

I would like to thank the reviewers for their extensive reviews.

I would first like to address the main point of critisism voiced
mainly by Review 4 but also by Review 2, that the survey is of a very
limited "Semantic Web" and so is unlikely to be generalizeable.

This critisism is very valid and taken to heart. To understand the
constraints of the study, it is first important to note that it is
directed at the community that convenes at ESWC. Also, such a paper
could address what this community does, what it can do, and what it
should do. We have consciously avoided strong "should do"
recommendations, except in the case where current practice is clearly
misguided. Most recommendations are therefore of the much softer "can
do" type, but the overall focus of the paper is on what the community
does.

Consequently, this survey is not meant to be generalizeable beyond the
current state of the art. I find it quite likely that the current
state must change in order for the Semantic Web to be successful, and
if the Semantic Web succeeds, the current conclusions will most
certainly not hold. The scope of the survey is a snapshot, confined to
what this community can reasonably do something about, and currently,
we are such a tiny fraction of the Web, that we have to understand the
Web better to succeed.

This survey is not intended as means to understand what the rest of
the Web is doing right and wrong, that wisdom is available elsewhere
in the broader literature, but since I believe a survey paper should
focus mostly on "does", it was not within my scope, nor the pagelimit,
to cite. This wisdom was therefore only cited from the standards.

The intention is mostly to have empirical research to see if 
statements like "it is no point in using caches when evaluating SPARQL
queries, since no endpoints are exposing them" have merit.

Review 1 asked us to discuss the importance of caching metadata for
query processing. We believe this is inappropriate for two reasons,
one is the "does" focus of the paper, but more importantly, this is
largely unknown at present. The study by Lampo et al, cited among
related work, provides a sobering account, and cautions us to not
oversell the importance of caching for query processing.

Review 4 pointed out a flaw in that the Surrogates header was
wrong. We acknowledge the error, and reran the spider recording the
Surrogate-Capability header instead, but it was not found, and thus
does not influence the conclusions.

### 2015-02-19 sanity/rebuttal.txt

I would like to thank the reviewers for their extensive reviews.

I would first like to address the main point of critisism voiced
mainly by Review 4 but also by Review 2, that the survey is of a very
limited "Semantic Web" and so is unlikely to be generalizeable.

This critisism is very valid and taken to heart. To understand the
constraints of the study, it is first important to note that it is
directed at the community that convenes at ESWC. Also, such a paper
could address what this community does, what it can do, and what it
should do. I have consciously avoided strong "should do"
recommendations, except in the case where current practice is clearly
misguided. Most recommendations are therefore of the much softer "can
do" type, but the overall focus of the paper is on what the community
does.

@@

Consequently, this survey is not meant to be generalizeable beyond the
current state of the art. I find it quite likely that the current
state must change in order for the Semantic Web to be successful, and
if the Semantic Web succeeds, the current conclusions will most
certainly not hold. The scope of the survey is a snapshot, confined to
what this community can reasonably do something about, and currently,
we are such a tiny fraction of the Web, that we have to understand the
Web better to succeed.

This survey is not intended as means to understand what the rest of
the Web is doing right and wrong, that wisdom is available elsewhere
in the broader literature, but since I believe a survey paper should
focus mostly on "does", it was not within my scope, nor the pagelimit,
to cite. This wisdom was therefore only cited from the standards.

The intention is mostly to have empirical research to see if 
statements like "it is no point in using caches when evaluating SPARQL
queries, since no endpoints are exposing them" have merit.

Review 1 asked us to discuss the importance of caching metadata for
query processing. I believe this is inappropriate for two reasons,
one is the "does" focus of the paper, but more importantly, this is
largely unknown at present. The study by Lampo et al, cited among
related work, provides a sobering account, and cautions us to not
oversell the importance of caching for query processing.

As this is an broad area of critisism from several reviews, I
shall attempt to condense the above discussion into a concise
clarification in the paper.

Review 4 pointed out a flaw in that the Surrogates header was
wrong. I acknowledge the error, and reran the spider recording the
Surrogate-Capability header instead, but it was not found, and thus
does not influence the conclusions, but I'll fix this.

### 2015-02-19 sanity/rebuttal.txt

Review 1 asked us to discuss the importance of caching metadata for
query processing. I believe this is inappropriate for two reasons,
one is the "does" focus of the paper, but more importantly, this is
largely unknown at present. The study by Lampo et al, cited among
related work, provides a sobering account, and cautions us to not
oversell the importance of caching for query processing.

As this is an broad area of critisism from several reviews, I
shall attempt to condense the above discussion into a concise
clarification in the paper.

Review 4 pointed out a flaw in that the Surrogates header was
wrong. I acknowledge the error, and reran the spider recording the
Surrogate-Capability header instead, but it was not found, and thus
does not influence the conclusions, but I'll fix this.

I note that the paper is very close to the page limit, so I would have
to remove parts of the paper to be able to expand on other parts. In
fact, I removed discussions relevant to the questions raised by Review
3 from the initial draft as they felt to deviate from the focus too
much.

Another example of things I removed was a list of the contributions,
as requested by Review 6, as I felt it was merely a reiteration of the
objectives that didn't not serve to clarify the paper, for any other
reason than convention.

Review 6 suggests that I use a logarithmic scale in some of the
figures. I initially did this, but felt that they didn't effectively
convey the essence, and that the problem is that our time and calendar
doesn't follow linear progression either. Therefore, one is left with
the choice of a classification that doesn't make intuitively sense or
one that doesn't make sense mathematically. I'll try out the
suggestion of combining the two.

I'll discuss these issues with local faculty to find a good solution.

Review 6 also suggests that I restructure the paper, and focus the
discussion. With a focused discussion, it may be room to do some
expansions of other points. I'll try my best, but it does not seem
straightforward to include all the elaborations requested by the
reviewers within the page limit.

Details:

Review 6 requests data published. I shall publish the data and the
code in a tar archive.

### 2015-02-19 sanity/rebuttal.txt

Consequently, this survey is not meant to be generalizeable beyond the
current state of the art. I find it quite likely that the current
state must change in order for the Semantic Web to be successful, and
if the Semantic Web succeeds, the current conclusions will most
certainly not hold. The scope of the survey is a snapshot, confined to
what this community can reasonably do something about, and currently,
we are such a tiny fraction of the Web, that we have to understand the
Web better to succeed.

This survey is not intended as means to understand what the rest of
the Web is doing right and wrong, that wisdom is available elsewhere
in the broader literature, but since I believe a survey paper should
focus mostly on "does", it was not within my scope, nor the pagelimit,
to cite. This wisdom was therefore only cited from the standards.

The intention is mostly to have empirical research to see if 
statements like "it is no point in using caches when evaluating SPARQL
queries, since no endpoints are exposing them" have merit.

Review 1 asked us to discuss the importance of caching metadata for
query processing. I believe this is inappropriate for two reasons, one
is the "does" focus of the paper, but more importantly, this is
largely unknown at present, and it cannot be inferred from a survey
alone. The study by Lampo et al, cited among related work, provides a
sobering account, and cautions us to not oversell the importance of
caching for query processing.

@@

As this is an broad area of critisism from several reviews, I
shall attempt to condense the above discussion into a concise
clarification in the paper.

Review 4 pointed out a flaw in that the Surrogates header was wrong. I
acknowledge the error, and reran the spider recording the
Surrogate-Capability header instead. It was not found, and therefore
the flaw does not influence the conclusions, but I'll fix this.

### 2015-02-19 sanity/rebuttal.txt

Review 6 suggests that I use a logarithmic scale in some of the
figures. I initially did this, but felt that they didn't effectively
convey the essence, and that the problem is that our time and calendar
doesn't follow linear progression either. Therefore, one is left with
the choice of a classification that doesn't make intuitively sense or
one that doesn't make sense mathematically. I'll try out the
suggestion of combining the two.

I'll discuss these issues with local faculty to find a good solution.

Review 6 also suggests that I restructure the paper, and focus the
discussion. With a focused discussion, it may be room to do some
expansions of other points. I'll try my best, but it does not seem
straightforward to include all the elaborations requested by the
reviewers within the page limit.

I'm not sure how to address the comment of Review 1 that the survey is
weak because it is based on only two documents. I assume they refer to
the two RFCs. First, it is not entirely true, it also references other
documents, only to show it is not widely used. Moreover, the two
documents defines the entire standards-based caching infrastructure of
the Web, as such, the survey is exhaustive.

Review 6 requests data to be published. I shall publish the data and
the code in a tar archive.

The reviewers provided detailed editorial comments that I shall take
into account when creating a camera ready version. I'll try to find a
native English writer to review the paper.

### 2015-02-21 sanity/rebuttal.txt

I would like to thank the reviewers for their extensive reviews.

I would first like to address the main point of critisism voiced
mainly by Review 4 but also by Review 2, that the survey is of a very
limited "Semantic Web" and so is unlikely to be generalizeable.

This critisism is very valid and taken to heart. To understand the
constraints of the study, it is first important to note that it is
directed at the community that convenes at ESWC. Also, such a paper
could address what this community does, what it can do, and what it
should do. I have consciously avoided strong "should do"
recommendations, except in the case where current practice is clearly
misguided. Most recommendations are therefore of the much softer "can
do" type, but the overall focus of the paper is on what the community
does.

Consequently, this survey is not meant to be generalizeable beyond the
current state of the art. I find it quite likely that the current
state must change in order for the Semantic Web to be successful, and
if the Semantic Web succeeds, the current conclusions will most
certainly not hold. In particular, there is nothing on the Web today
that supports query evaluation in the way that a large-scale
deployment of federated SPARQL would. The scope of the survey is a
snapshot, confined to what this community can reasonably do something
about, and currently, we are such a tiny fraction of the Web, that we
have to understand the Web better to succeed.

@@

Review 6 suggests that I use a logarithmic scale in some of the
figures. I initially did this, but felt that they didn't effectively
convey the essence, and that the problem is that our time and calendar
doesn't follow linear progression either. Therefore, one is left with
the choice of a classification that doesn't make intuitively sense or
one that doesn't make sense mathematically. I'll try out the
suggestion of combining the two.

I'll discuss these issues with local faculty to find a good solution.

Review 6 also suggests that I restructure the paper, and focus the
discussion. With a focused discussion, it may be room to do some
expansions of other points. I'll try my best, but it does not seem
straightforward to include all the elaborations requested by the
reviewers within the page limit.

I'm not sure how to address the comment of Review 1 that the survey is
weak because it is based on only two documents. I assume they refer to
the two RFCs. First, it is not entirely true, it also references other
documents, only to show that they are not widely used. Moreover, the
two documents defines the entire standards-based caching
infrastructure of the Web, as such, the survey is exhaustive.

### 2015-02-21 sanity/rebuttal.txt

I would like to thank the reviewers for their extensive reviews.

I would first like to address the main point of critisism voiced
mainly by Review 4 but also by Review 2, that the survey is of a very
limited "Semantic Web" and so is unlikely to be generalizeable.

This critisism is very valid and taken to heart, and I should strive
to make it clearer why this is the scope I chose to work within.
Indeed, this Semantic Web is a mere fraction of the open data web,
where e.g. JSON APIs are common. Coffee break discussions around
caching have often stranded on the lack of data around what the
community as a whole actually does, and therefore, that is the main
focus of this paper. What it can do is given some space, but a
discussion of what it should do is consciously avoided, except in the
case where current practice is clearly misguided. Since the paper
already fills the pagelimit, I have only cited the foundational
documents for wisdom on what is thought to be important for the Web, a
further discussion would be beyond the available space, and probably
also be better suited for a different conference.

Review 1 asked us to discuss the importance of caching metadata for
query processing. This is the focus our research, but this is
largely unknown at present, and it cannot be inferred from a survey
alone. The study by Lampo et al, cited among related work, provides a
sobering account, and cautions us to not oversell the importance of
caching for query processing.

Review 4 pointed out a flaw in that the Surrogates header was wrong. I
acknowledge the error, and will rerun the spider.

I note that the paper is very close to the page limit, and amongst the
things that were removed from the initial draft are discussions of the
questions raised by Review 3 and a list of the contributions, as
requested by Review 6. Review 6 suggest that I focus the discussion,
which could reduce the length somewhat, but I would welcome
suggestions on what else could be trimmed, to make room for
elaborations suggested in the reviews.

I initially used logarithmic scale as suggested by Review 6, for the
reasons they mention. I found the intuitive interpretation of the
figures to be very difficult, since the time and calendar scale is as
it is. The suggestion to combine the two is interesting, and I will
see if provides any benefit if the paper is accepted.

### 2015-02-21 sanity/rebuttal.txt

I would like to thank the reviewers for their extensive reviews. The
many editorial advices will certainly be taken into account without
further comment.

The critisism that I only surveyed a small part of the Web and so, the
conclusions are not generalizeable is valid, and I should strive to
make it clearer why this is the scope I chose to work within. Indeed,
this Semantic Web is a mere fraction of the open data web, where
e.g. JSON APIs are common. Coffee break discussions around caching
have often stranded on the lack of data around what the community as a
whole actually does, and therefore, that is the main focus of this
paper. What it can do is given some space, but a discussion of what it
should do is consciously avoided, except in the case where current
practice is clearly misguided. Since the paper already fills the
pagelimit, I have only cited the foundational documents for wisdom on
what is thought to be important for the Web, a further discussion
would be beyond the available space.

@@

Review 1 asked us to discuss the importance of caching metadata for
query processing. This is the focus our research, but this is
largely unknown at present, and it cannot be inferred from a survey
alone. The study by Lampo et al, cited among related work, provides a
sobering account, and cautions us to not oversell the importance of
caching for query processing.

Review 4 pointed out a flaw in that the Surrogates header was wrong. I
acknowledge the error, and have rerun the spider.

I note that the paper is very close to the page limit, and amongst the
things that were removed from the initial draft are discussions of the
questions raised by Review 3 and a list of the contributions, as
requested by Review 6. Review 6 suggest that I focus the discussion,
which could reduce the length somewhat, but I would welcome
suggestions on what else could be trimmed, to make room for
elaborations suggested in the reviews.

I initially used logarithmic scale as suggested by Review 6, for the
reasons they mention. I found the intuitive interpretation of the
figures to be very difficult, since the time and calendar scale is as
it is. The suggestion to combine the two is interesting, and I will
see if it provides any benefit if the paper is accepted.

I'm not sure how to address the comment of Review 1 that the survey is
weak because it is based on only two documents. I assume they refer to
the two RFCs. First, it is not entirely true, see Table 1. Moreover,
the two documents define the entire standards-based caching
infrastructure of the Web, as such, the survey is exhaustive.

### 2015-02-21 sanity/rebuttal.txt

I would like to thank the reviewers for their extensive reviews. The
many editorial advices will certainly be taken into account without
further comment.

The critisism that I only surveyed a small part of the Web and so, the
conclusions are not generalizeable is valid, and I should strive to
make it clearer why this is the scope I chose to work within. Indeed,
this Semantic Web is a mere fraction of the open data web, where
e.g. JSON APIs are common. ISWC/ESWC coffee break discussions around
caching have often stranded on the lack of data around what the
community as a whole actually does, and therefore, that is the main
focus of this paper. The recommendations are meant as suggestions on
what the community may do, but a discussion of what it should do is
consciously avoided, except in the case where current practice is
clearly misguided. Since the paper already fills the pagelimit, I have
only cited the foundational documents for wisdom on what is thought to
be important for the Web, a further discussion would be beyond the
available space.

@@

Review 1 asked us to discuss the importance of caching metadata for
query processing. This is the focus our research, but this is
largely unknown at present, and it cannot be inferred from a survey
alone. The study by Lampo et al, cited among related work, provides a
sobering account, and cautions us to not oversell the importance of
caching for query processing.

Review 4 pointed out a flaw in that the Surrogates header was wrong. I
acknowledge the error, and have rerun the spider.

I note that the paper is very close to the page limit, and amongst the
things that were removed from the initial draft are discussions of the
questions raised by Review 3 and a list of the contributions, as
requested by Review 6. Review 6 suggest that I focus the discussion,
which could reduce the length somewhat, but I would welcome
suggestions on what else could be trimmed, to make room for
elaborations suggested in the reviews.

I initially used logarithmic scale as suggested by Review 6, for the
reasons they mention. Then, I found the intuitive interpretation of
the figures to be very difficult, since the time and calendar scale is
as it is. The suggestion to combine the two is interesting, and I will
see if it provides any benefit if the paper is accepted.

### 2015-02-21 sanity/paper1.tex
Useable metadata; reorder Section refs
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1038 43ef1190-90fd-4dd7-a769-d0121f02b80e

RFC7234 defines two important headers: \httph{Expires}, whose value is
a date and time of when the response is considered stale, and
therefore should not be used; and \httph{Cache-Control}, which allows
detailed control of the cache, including a \httph{max-age} field,
which gives the time in seconds for how long the the response may be
used from the time of the request. \httph{max-age} takes precedence
over \httph{Expires}. In the following \emph{freshness lifetime} is
understood as the number of seconds that the response may be used
without contacting the origin server. Ideally, the calculation of the
freshness lifetime should be based of the above, we therefore shall
refer to this as ``standards-compliant caching''. However it can also
be based on heuristics, and RFC7234, Section~4.2.2 provides some loose
constraints for such practice, as well as a suggestion for a useful
heuristic. This heuristic is based on a fraction of the time lapsed
between the current time and the modification time given in the
\httph{Last-Modified} header. This approach therefore still requires
the Web server to be cooperative to be successful. Commonly, Web
servers can track this, for example if RDF is served from a file
system the file modification time is used.

@@

First, we investigated whether certain server implementations provided
better support for caching than others. To do this, we formulated
SPARQL queries to examine the \httph{Server} headers of successful
responses, with optional clauses matching the standards-compliant
computed freshness lifetime (which is the ideal) as well as whether
the response had other promising features that may assist caching such
as modification time, certain predicates, etc.%\todo{promising}

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness lifetime or a promising feature. For
the former, this amounted to 22 servers. 70 servers always responded
with promising features. Inspecting the values we find the well-known
Virtuoso and Callimachus servers, as well as the Perl modules
RDF::LinkedData and RDF::Endpoint, which is partly developed by and
runs on a server operated by this author. Apart from those, a typical
server string is e.g. \httph{Apache/2.2.22 (Fedora)}, which reveals
very little about the RDF-specific parts of the underlying server
implementation. A quick inspection of all \httph{Server} headers
confirmed that few reveal any further detail.

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others.
Using the methodology given in Appendix~\ref{app:stats}, we find in
both the cases of standards-compliant freshness lifetime and for the other
promising features, the test reports \pvalue = 0.0001. We can conclude
that it is highly likely that some servers are better at exposing
cache headers than others. Unfortunately, since most \httph{Server}
headers only contain generic values, little can be learnt about these
implementations. We note, however, that DBPedia exposes
standards-compliant freshness lifetime of 604800 seconds (i.e. 1 week) for
both LOD and SPARQL endpoints.

@@

We next consider the simple heuristic freshness lifetime as suggested in
RFC7234, Section~4.2.2 and mentioned in the introduction.

@@

In this work, we have only explored the cases where the server is
cooperative, in the sense that message data or metadata provides at
least a hint of a resource's cacheability. We also noted that the
majority of the Semantic Web is unhelpful. Therefore, an interesting
direction is to learn the change frequency of resources to use in a
heuristic freshness lifetime estimation. However, such work should
operate within the loose constraints of RFC7234, Section~4.2.2, and
should find its niche when the other techniques described in this paper
are unavailable. Once this is done, the correctness of caching headers
should be assessed, possibly using contingency tables similar to those
in Appendix~\ref{app:stats}.

>>>>

RFC7234 defines two important headers: \httph{Expires}, whose value is
a date and time of when the response is considered stale, and
therefore should not be used; and \httph{Cache-Control}, which allows
detailed control of the cache, including a \httph{max-age} field,
which gives the time in seconds for how long the the response may be
used from the time of the request. \httph{max-age} takes precedence
over \httph{Expires}. In the following \emph{freshness lifetime} is
understood as the number of seconds that the response may be used
without contacting the origin server. Ideally, the calculation of the
freshness lifetime should be based of the above, we therefore shall
refer to this as ``standards-compliant caching''. However it can also
be based on heuristics, and Section~4.2.2 in RFC7234 provides some loose
constraints for such practice, as well as a suggestion for a useful
heuristic. This heuristic is based on a fraction of the time lapsed
between the current time and the modification time given in the
\httph{Last-Modified} header. This approach therefore still requires
the Web server to be cooperative to be successful. Commonly, Web
servers can track this, for example if RDF is served from a file
system the file modification time is used.

@@

First, we investigated whether certain server implementations provided
better support for caching than others. To do this, we formulated
SPARQL queries to examine the \httph{Server} headers of successful
responses, with optional clauses matching the standards-compliant
computed freshness lifetime (which is the ideal) as well as whether
the response had other indications of caching-related metadata that
may assist caching such as modification time, certain predicates, etc.

For each unique \httph{Server} header, we found the ones where
\emph{all} responses had a freshness lifetime or other usable metadata. For
the former, this amounted to 22 servers. 70 servers always responded
with usable metadata. Inspecting the values we find the well-known
Virtuoso and Callimachus servers, as well as the Perl modules
RDF::LinkedData and RDF::Endpoint, which is partly developed by and
runs on a server operated by this author. Apart from those, a typical
server string is e.g. \httph{Apache/2.2.22 (Fedora)}, which reveals
very little about the RDF-specific parts of the underlying server
implementation. A quick inspection of all \httph{Server} headers
confirmed that few reveal any further detail.

For a more systematic approach, we wish to test the hypothesis that
some servers are better configured to support caching than others.
Using the methodology given in Appendix~\ref{app:stats}, we find in
both the cases of standards-compliant freshness lifetime and for the other
usable metadata, the test reports \pvalue = 0.0001. We can conclude
that it is highly likely that some servers are better at exposing
cache headers than others. Unfortunately, since most \httph{Server}
headers only contain generic values, little can be learnt about these
implementations. We note, however, that DBPedia exposes
standards-compliant freshness lifetime of 604800 seconds (i.e. 1 week) for
both LOD and SPARQL endpoints.

@@

We next consider the simple heuristic freshness lifetime as suggested in
Section~4.2.2 in RFC7234 and mentioned in the introduction.

@@

In this work, we have only explored the cases where the server is
cooperative, in the sense that message data or metadata provides at
least a hint of a resource's cacheability. We also noted that the
majority of the Semantic Web is unhelpful. Therefore, an interesting
direction is to learn the change frequency of resources to use in a
heuristic freshness lifetime estimation. However, such work should
operate within the loose constraints of Section~4.2.2 in RFC7234, and
should find its niche when the other techniques described in this paper
are unavailable. Once this is done, the correctness of caching headers
should be assessed, possibly using contingency tables similar to those
in Appendix~\ref{app:stats}.
